---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# location

<!-- badges: start -->
[![R-CMD-check](https://github.com/hypertidy/location/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/location/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Minimal geocoding for R via [Nominatim](https://nominatim.openstreetmap.org/) (OpenStreetMap). No API key required.

## Installation

```r
pak::pak("hypertidy/location")
```

## Usage

```{r location}
library(location)

# Single place
loc("Hobart, Tasmania")

# Multiple places - one request per second (Nominatim policy)
loc(c("Davis Station, Antarctica", "Casey Station", "Mawson Station"))

# Straight to timezone (requires lutz)
loc_tz("Crystal Lake, TN")

loc_tz(c("Hobart", "McMurdo Station", "Rothera"))
```

## Design

- `loc(x)` → data frame: `query`, `lat`, `lon`, `display_name`, `osm_type`
- `loc_tz(x)` → character vector of IANA tz names (requires `lutz`)
- `full = TRUE` returns all Nominatim response fields
- `api_url` can point to a local Nominatim instance
- Enforces 1 req/sec and sets a meaningful `User-Agent` per [Nominatim policy](https://operations.osmfoundation.org/policies/nominatim/)
- `curl::has_internet()` guard — returns `NA` rows silently offline

## Used by

- [hypertidy/timenow](https://github.com/hypertidy/timenow) — timezone-aware timestamps
- [msumner/place](https://github.com/msumner/place) — place name utilities

## Dependencies

- `curl` — HTTP
- `jsonlite` — JSON parsing
- `lutz` (suggested) — for `loc_tz()`


## Code of Conduct
  
Please note that the location project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
